\section*{Exercise (iv)}

Assuming $V^0(t,x) = x$ and then showing that the two PDEs coincide we have shown $V^0(t,x) = x$.

From Proposition~3.3, assuming $V^0(t,x)$ is sufficiently differentiable and conditioning
on $j=0$, the market reserve satisfies the PDE
\begin{equation}\label{eq:prop33_pde}
  V_t^0(t, x) = rV^0(t, x) - b^0(t, x) - \mu(t)R^{01}(t, x) - \mathcal{D}_x V^0(t, x),
\end{equation}
where $V^1(t,x) \equiv 0$, yielding
\[
  R^{01}(t, x) = b^{01}(t, x) - V^0(t, x),
\]
and the operator $\mathcal{D}_x$ is given by
\[
  \mathcal{D}_x V^0(t, x) = V_x^0(t, x) (rx - a^0(t,x) - \mu(t)\varrho^{01}(t,x)) + \frac{1}{2}V_{xx}^0(t, x)\pi^2(t, x)\sigma^2 x^2,
\]
Note in our case: $\varrho^{01}(t,x) = a^{01}(t,x) - x$.
\\
\\
Since the contract features no discrete jumps in benefits or account balance, the jump condition (3.7b) is satisfied.
\\
\\
For $V^0(t,x) = x$ we find the derivatives.
\[
  V_t^0 = 0, \qquad V_x^0 = 1, \qquad V_{xx}^0 = 0.
\]
Substituting these into the operator yields $\mathcal{D}_x V^0(t, x) =  rx - a^0(t,x) - \mu(t)\varrho^{01}(t,x)$ and $R^{01}(t,x) = b^{01}(t,x) - x$. 
The PDE~\eqref{eq:prop33_pde} thus simplifies to:

\begin{align*}
  V_t^0(t, x) &= rV^0(t, x)-rx = r(x-x) = 0.
\end{align*}



\subsection*{Active phase, $t \in [30, m)$}

During the active phase, premiums are paid at rate $\theta L(t)$ (a negative benefit) and the death benefit is $K L(t)$. Thus, the actual contractual benefits are:
\[
  b^0(t,x) = -\theta L(t), \qquad b^{01}(t,x) = K L(t).
\]
From SDE~(1), substituting the physical expected return $\tilde{r}(t)$ with the risk-free rate $r$, the risk-neutral drift of the account is
\[
  A(t,x) = r\,x + \theta L(t) - \mu(t)\bigl(KL(t)-x\bigr).
\]
We verify~\eqref{eq:thiele_reduced} by evaluating the right-hand side:
\begin{align*}
  r x - b^0(t,x) - \mu(t)\bigl(b^{01}(t,x) - x\bigr) 
  &= r x - \bigl(-\theta L(t)\bigr) - \mu(t)\bigl(K L(t) - x\bigr) \\
  &= r x + \theta L(t) - \mu(t)\bigl(K L(t) - x\bigr) \\
  &= A(t,x). \quad\checkmark
\end{align*}

\subsection*{Retirement phase, $t \in [m, 111]$}

During retirement, the account pays a continuous annuity rate $x / \tilde{V}^0(t)$, and the account is forfeited to the mutual pool upon death (no death benefit). Thus:
\[
  b^0(t,x) = \frac{x}{\tilde{V}^0(t)}, \qquad b^{01}(t,x) = 0.
\]
From SDE~(2), the account growth includes a survivorship dividend $\mu(t)x$ from the mortality pool. Changing $\tilde{r}(t)$ to $r$, the risk-neutral drift is
\[
  A(t,x) = \bigl(r+\mu(t)\bigr)x - \frac{x}{\tilde{V}^0(t)}.
\]
We verify~\eqref{eq:thiele_reduced} by evaluating the right-hand side:
\begin{align*}
  r x - b^0(t,x) - \mu(t)\bigl(b^{01}(t,x) - x\bigr) 
  &= r x - \frac{x}{\tilde{V}^0(t)} - \mu(t)\bigl(0 - x\bigr) \\
  &= r x - \frac{x}{\tilde{V}^0(t)} + \mu(t) x \\
  &= \bigl(r+\mu(t)\bigr)x - \frac{x}{\tilde{V}^0(t)} \\
  &= A(t,x). \quad\checkmark
\end{align*}

\subsection*{Boundary condition}

At the terminal age $n=111$ there are no future obligations, so equation (3.7c) requires the boundary condition $V^0(111,x) = 0$. If $V^0(t,x) = x$, this means we need $X(111) = 0$.

This is guaranteed by the construction of the calculation basis: the reserve $\tilde{V}^0(t)$ computed in Exercise~(i) satisfies $\tilde{V}^0(111)=0$. Thus, the annuity payout rate $X(t)/\tilde{V}^0(t) \to \infty$ as $t\to 111$, which drains the account completely. The purpose of $\tilde{V}^0$ is precisely to calibrate the payout rate so that the account is exhausted at the maximum age. The simulation from Exercise~(ii) confirms this numerically: $X(111)\approx 0$, thereby satisfying (3.7c).

\subsection*{Conclusion}

Proposition~3.3 states that, conversely, if there exists a set of functions $V^j(t,x)$ such that conditions (3.7) hold, then the function is indeed equal to the reserve. By explicitly verifying that $V^0(t,x)=x$ satisfies the PDE (3.7a) in both phases, the trivial jump condition (3.7b), and the terminal condition (3.7c), we conclude that
\[
  \boxed{V^0(t,x) = x.}
\]
The market reserve equals the account value. This is the defining property of a unit-link product: the policyholder bears all investment risk, and the account dynamics are constructed to continuously budget for every mortality and benefit cash flow, making the account the exact self-financing replicating portfolio for all future obligations.

